\documentclass[a4paper,11pt]{article}
\usepackage{sobrapo-template}
\usepackage[brazil]{babel}
\usepackage[latin1]{inputenc}
\usepackage{amsmath,amssymb}

\usepackage{indentfirst}

\title{An Incomplete Overview of some Applications of Game Theory to Patient Flow}

\begin{document}

\maketitle

\author{
\name{Vincent Knight}
\institute{Cardiff University}
\iaddress{Cardiff, UK}
\email{knightva@cf.ac.uk}
}

\author{
\name{Paul Harper}
\institute{Cardiff University}
\iaddress{Cardiff, UK}
\email{harper@cf.ac.uk}
}

\author{
\name{Jeff Griffiths}
\institute{Cardiff University}
\iaddress{Cardiff, UK}
\email{griffiths@cf.ac.uk}
}

\author{
\name{Izabela Komenda}
\institute{Cardiff University}
\iaddress{Cardiff, UK}
\email{komendai@cf.ac.uk}
}

\vspace{8mm}

\begin{abstract}
Describe paper.
\end{abstract}

\bigskip
\begin{keywords}
Patient Flow, Game Theory, Queueing Theory

\bigskip
\noindent{Main Area: Healthcare}
\end{keywords}


\newpage

\section{Introduction}

\begin{itemize}
    \item Review GT in HC in general (small);
    \item Review congestion type games;
    \item PoA;
    \item Structure.
\end{itemize}

\section{Choosing queues}

\begin{itemize}
    \item PoA in healthcare paper;
    \item Rob's work
\end{itemize}

\section{CCU Work}

\begin{itemize}
    \item IK Paper
\end{itemize}

\section{EU and EMV Interface}

\begin{itemize}
    \item Describe model;
    \item Show some results.
\end{itemize}

\section{Conclusions}

\bigskip
\noindent{\bf Refer\^encias}

\noindent \textbf {Anna, A.} (1996), Comunica\c c\~ao, \textit{Atas do XXVIII SBPO}, 123-134.

\noindent \textbf{Gates, B.}, \textit{Um Livro Muito Bom}, Editor, Local, 2003.

\noindent  \textbf{Pel\'e, E. N. e Rom\'ario, R. R.}, Exemplo de artigo em livro, em Windows, P. T. e Linux, V. G. (Eds.),
\textit{Colet\^ania de Artigos},  Editor, Local, 123-133, 2004.

\noindent  \textbf{Silva, A. B., Souza, C. D. e Santos, E. F.}, T\'\i tulo de um relat\'orio t\'ecnico dispon\'\i vel na Internet,
\textit{ Relat\'orios de Pesquisa em Engenharia de Produ\c c\~ao}, n. 4,  Universidade Z,
1999

\noindent{(www.universidade.br/rel, 4, 2001.}

\noindent  \textbf{Smith, S. e Jones, J.} (2002), A paper on Operations Research, \textit{Pesquisa Operacional},
32, 5-44.

\end{document}


